Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
luis fixes

\Luis{A primeira threat que falas é que os resultados podem nao generalizar
para software fechado. Eu acho que deviamos ser mais diretos.}\Sof{Diretos como?}

This study uses a dataset that only covers
open-source software to perform the maintainability evaluation. However, BCH
thresholds are calculated from a set of both open and closed software.
Different programming languages may require different coding practices to
address software safety. The dataset comprises more commits in C and PHP, i.e.,
the dataset may not be properly representative of the population regarding to programming languages.

@@

\Luis{pode ser uma cena só minha mas acho que fica melhor em vez de comecar
fraseds com "And," usar outros conetores tipo "Besides," "In addition,", etc. œ}

Many studies have investigated the relationship between refactorings and software quality.
Previous work focused on coupling metrics has evaluated the impact of refactorings and
exhibited proof that quantifying effectively the impact of refactoring on maintainability
may help to choose the appropriate refactoring type~\cite{1167822}. In contrast to
this work, Hegedus et al.~\cite{HEGEDUS2018313} did not select particular metrics to
assess the effect of refactorings. Instead, statistical tests were used to find
the metrics that have the potential to change significantly after refactorings.
The differences of maintainability between groups of refactored elements and
non-refactored were analyzed. And, the authors conclude that the source
code elements subjected to refactorings had significantly lower maintainability
than the elements not affected. Studying the evolution of maintaninability issues during the development of Android apps, Malavolta et al. (2018)~\cite{8530041} discovered that maintainability
decreases over time. Palomba et al. (2018)~\cite{Palomba:2018:DIM:3231288.3231337} exhibits
proof that code smells should be carefully monitored by programmers, since there is
a high correlation between maintainability aspects and proneness to changes and faults.
The present work is based on the 10 guidelines proposed
by the Software Improvement Group (SIG) and focuses solely on evaluating
the impact of patching vulnerabilities on software maintainability.

\Luis{eu nao acho que usar 10 guidelines proposed by the Software Improvement
Group (SIG) seja algo que nos esteja a diferenciar. Acho que o a prinicpal
diferenca é que estamos a estudar maintainability issues noutro contexto.}

@@

Other studies investigated the effect of programming languages in software quality~\cite{Ray:2017:LSP:3144574.3126905,
2019arXiv190110220B}. The first study shows that some programming languages are more buggy than others, i.e.,
language design has impact on software quality. However, the authors of the second
study were not able to reproduce the first one and did not obtain any evidence about the
impact of language design. Both have used the number of defects as an indicator of
software quality. The present work studies how security refactorings affect software quality
based on the code maintainability analysis.

\Luis{ tambem fizemos analise por linguagem, nesta ultima citacao deviamos falar sobre isso tb.}

@@

\Luis{secure security frameworks, nao percebi bem o que se quer dizer aí.}

This study also exhibits evidence that some patterns need more attention than
others. \emph{Broken Autentication} issues, \emph{Denial-of-Service} attacks and \emph{Memory Leaks}
endure maintainability in 55.3\%, 51.3\% and 47.5\%, respectively. Following
the implications of our work, we draw attention for the need of secure security
frameworks, code best practices documentation to produce safe and maintainable
code, proper authorization mechanisms design and implementation, better tools
to introduce in the CI/CD pipeline to help software maintenance and new or
improved programming languages to allow developers to easily implement safety
in their software without endangering maintainability.

>>>>

\Luis{A primeira threat que falas é que os resultados podem nao generalizar
para software fechado. Eu acho que deviamos ser mais diretos.}
\Sof{Melhor?}

We use a dataset that only comprises refactorings of open-source software. However, the methodology requires to access data that is not publicly available. Thus, our findings may not extent to non-open source software.

Different programming languages may require different coding practices to
address software safety. The dataset comprises more commits in C and PHP, i.e.,
the dataset may not be properly representative of the population regarding to programming languages.

@@

Many studies have investigated the relationship between refactorings and software quality.
Previous work focused on coupling metrics has evaluated the impact of refactorings and
exhibited proof that quantifying effectively the impact of refactoring on maintainability
may help to choose the appropriate refactoring type~\cite{1167822}. In contrast to
this work, Hegedus et al.~\cite{HEGEDUS2018313} did not select particular metrics to
assess the effect of refactorings. Instead, statistical tests were used to find
the metrics that have the potential to change significantly after refactorings.
The differences of maintainability between groups of refactored elements and
non-refactored were analyzed. In addition, the authors conclude that the source
code elements subjected to refactorings had significantly lower maintainability
than the elements not affected. Studying the evolution of maintaninability issues during the development of Android apps, Malavolta et al. (2018)~\cite{8530041} discovered that maintainability
decreases over time. Palomba et al. (2018)~\cite{Palomba:2018:DIM:3231288.3231337} exhibits
proof that code smells should be carefully monitored by programmers, since there is
a high correlation between maintainability aspects and proneness to changes and faults.
The present work uses a model proposed by BCH and focuses solely on evaluating
the impact of patching vulnerabilities on software maintainability.

\Luis{eu nao acho que usar 10 guidelines proposed by the Software Improvement
Group (SIG) seja algo que nos esteja a diferenciar. Acho que o a prinicpal
diferenca é que estamos a estudar maintainability issues noutro contexto.}\Sof{Melhor?}

@@

Other studies investigated the effect of programming languages in software quality~\cite{Ray:2017:LSP:3144574.3126905,
2019arXiv190110220B}. The first study shows that some programming languages are more buggy than others, i.e.,
language design has impact on software quality. However, the authors of the second
study were not able to reproduce the first one and did not obtain any evidence about the
impact of language design. Both have used the number of defects as an indicator of
software quality. The present work studies how security refactorings affect software quality
based on the code maintainability analysis and provides some evidence that the programming language has impact on maintainability.

\Luis{ tambem fizemos analise por linguagem, nesta ultima citacao deviamos falar sobre isso tb.}\Sof{Acho que esta!}

@@

\Luis{secure security frameworks, nao percebi bem o que se quer dizer aí.}
\Sof{Melhor?}

This study also exhibits evidence that some patterns need more attention than
others. \emph{Broken Autentication} issues, \emph{Denial-of-Service} attacks and \emph{Memory Leaks}
endure maintainability in 55.3\%, 51.3\% and 47.5\%, respectively. Following
the implications of our work, we draw attention for the need of trustfull security
frameworks, code best practices documentation to produce safe and maintainable
code, proper authorization mechanisms design and implementation, better tools
to introduce in the CI/CD pipeline to help software maintenance and new or
improved programming languages to allow developers to easily implement safety
in their software without endangering maintainability.
